Direct Spectral Detection: A Cheap Method to Detect and Characterize Binary Systems

### 2015-10-21 paper/ms.tex
Added units to Table 6 and Figure 8.
Updated title.
Done with referee comments!

\title{Direct Spectroscopic Detection: A Cheap Method to Detect and Characterize Binary Systems}

@@

The direct spectral detection method (hereafter referred to as the DSD method), and variations thereof, has been used to search for binary companions to early B-stars \citep{Gullikson2013}, main sequence FGK-stars \citep{Kolbl2015}, young K-M stars \citep{Prato2002}, and even `Hot Jupiter' type planets \citep{Snellen2010, Brogi2012, deKok2013} orbiting FGK-stars. The method relies on the cross-correlation function (CCF) of a high-spectral-resolution spectrum of the primary star with a model spectrum for the expected companion. Since the CCF uses every pixel in the spectrum, and more importantly every spectral line in the secondary spectrum, the detection significance increases approximately as $\sqrt{N}$, where N is the number of spectral lines. For high-resolution cross-dispersed \'echelle spectra, this amplification can reach factors of 10, allowing the detection \emph{and characterization} of a secondary spectrum where the individual lines are completely buried in noise. Since the DSD method uses a seeing-limited spectrum of the primary star, its sensitivity is independent of separation inside $\sim 1 ''$ and can make use of small telescopes to detect high-contrast companions.

@@

We now use the DSD method to measure the temperatures of several known binary systems (Table \ref{tab:known}). We cross-correlate the spectra against the full grid of model spectra enumerated in Section \ref{sec:method}, and find the temperature using Equation \ref{eqn:tmeas}. We then convert the measured temperature to PDFs of the true companion temperature using the MCMC chains developed in Section \ref{subsec:systematics} (see also Figure \ref{fig:error}). For stars with multiple observations, we multiply the PDFs from each detection. Finally, we calculate the companion temperature and confidence interval from the integral of the PDF:

@@

\newpage
\clearpage
\begin{deluxetable}{cccccccc}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablecaption{ Companion data \label{tab:measured}}
\tablehead{
\colhead{Primary} &  \multicolumn{3}{c}{Measured Values} &  \multicolumn{2}{c}{Expected Values} \\
\colhead{ Star} & \colhead{$\rm T_{eff}$} & \colhead{[Fe/H]} & \colhead{vsini} & \colhead{ $\rm T_{eff}$} & \colhead{ $v\sin{i}$}}

>>>>

\title{Direct Spectral Detection: A Cheap Method to Detect and Characterize Binary Systems}

@@

The direct spectral detection method (hereafter referred to as the DSD method), and variations thereof, has been used to search for binary companions to early B-stars \citep{Gullikson2013}, main sequence FGK-stars \citep{Kolbl2015}, young K-M stars \citep{Prato2002}, and even `Hot Jupiter' type planets \citep{Snellen2010, Brogi2012, deKok2013} orbiting FGK-stars. The method relies on the cross-correlation function (CCF) of a high-spectral-resolution spectrum of the primary star with a model spectrum for the expected companion. The CCF uses every pixel in the spectrum, and more importantly every spectral line in the secondary spectrum. A simple experiment with synthetic spectra containing increasing numbers of spectral lines (N) to noisy data shows that the CCF peak significance increases as $\sqrt{N}$. For high-resolution cross-dispersed \'echelle spectra, this amplification can reach several factors of 10, allowing the detection \emph{and characterization} of a secondary spectrum where the individual lines are completely buried in noise. Since the DSD method uses a seeing-limited spectrum of the primary star, its sensitivity is independent of separation inside $\sim 1 ''$ and can make use of small telescopes to detect high-contrast companions.

@@

We now use the DSD method to measure the temperatures of several known binary systems (Table \ref{tab:known}). We cross-correlate the spectra against the full grid of model spectra enumerated in Section \ref{sec:method}, and find the temperature of the companion using Equation \ref{eqn:tmeas}. We then convert the measured temperature to PDFs of the true companion temperature using the MCMC chains developed in Section \ref{subsec:systematics} (see also Figure \ref{fig:error}). For stars with multiple observations, we multiply the PDFs from each detection. Finally, we calculate the companion temperature and confidence interval from the integral of the PDF:

@@

\newpage
\clearpage
\begin{deluxetable}{cccccccc}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablecaption{ Companion data \label{tab:measured}}
\tablehead{
\colhead{} &  \multicolumn{3}{c}{Measured Values} &  \multicolumn{2}{c}{Expected Values} \\
\colhead{ Primary} & \colhead{$\rm T_{eff}$} & \colhead{[Fe/H]} & \colhead{vsini} & \colhead{ $\rm T_{eff}$} & \colhead{ $v\sin{i}$} \\
\colhead{Star} & \colhead{ (K)} & \colhead{(dex)} & \colhead{ (km s$^{-1}$)} & \colhead{(K)} & \colhead{ (km s$^{-1}$)}}
